\item Turn hardware on.
\item Observe that a stable video image is produced on VGA
\item Observe that a stable video image is produced on HDMI
  #[Should produce a stable video image on VGA in PAL and NTSC modes]  
  #[Should produce a stable video image on HDMI in PAL and NTSC modes]  
\item Observe that MEGA65 boots to BASIC 10
  #1
\item Observe that HDMI video image is centred both vertically and horizontally
  #146
\item Press the RESTORE key for 1 second.
\item Observe that the Freeze Menu appears
\item Observe that thumbnail image looks correct, and is not rotated in horizontal or vertical planes. 
\item Press V to toggle video mode to NTSC.
\item Press F3 to exit freeze menu
\item Observe that BASIC 10 resumes running
#158
\item Press RESTORE key for one second again, to re-enter Freeze Menu
\item Observe that there are options to select disk image for both “INTERNAL DRIVE” and “EXTERNAL 1565”.
\item Press 8 to change device number of internal drive from 8 to 10
\item Press 9 to change device number of external 1565 drive from 9 to 11
\item Press 0 to select a D81 disk image to mount on device 10.
\item Observe that the full list of D81 images you have on the SD card appear
\item Press 1 to select a different D81 disk image to mount on device 11
\item Press F3 to exit Freeze Menu
\item Type DIR U10, and confirm that the directory of the first D81 image displays.
\item Type DIR U11, and confirm that the directory of the second D81 image displays.
\item Type GO64 and Y to switch to C64 mode.
\item Load a game or other program that has working audio.
\item Press RESTORE key for one second to re-enter Freeze Menu
\item Press A to enter Audio Mixer.
\item Ensure that audio levels are set for all sound output channels that the hardware target supports. 

  XXX - Provide more detailed instructions for this step 
\item Press RUN/STOP and then F3 to exit Freeze Menu.
\item Listen for audio from the various output channels.
